--- 
title: "A Vulnerability Prediction Analysis"
author: "Luis Guerra"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
description: |
  I created this project with the aim to express how a vulnerability can be interpreted using a graphical representation based on a information sample dataset caught from antivirus public database.
---

```{r eval=TRUE}
library(forecast)
library(lubridate)
library(tidyverse)
library(readr)
library(markdown)
library(plotrix)
library(gganimate)
library(gifski)

Informe_de_virus <- read_delim("Informe de virus.csv",delim = ";", escape_double = FALSE, trim_ws = TRUE)
```

# About

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports; for example, a simple math equation $a^2 + b^2 = c^2$.

- readr
- dplyr
- stringr
- ggplot2
- tidyverse
- readxl
- qplot
- markdown

## Usage 

Each **bookdown** chapter is an .Rmd file, and each .Rmd file can contain one (and only one) chapter. A chapter *must* start with a first-level heading: `# A good chapter`, and can contain one (and only one) first-level heading.

Use second-level and higher headings within chapters like: `## A short section` or `### An even shorter section`.

The `index.Rmd` file is required, and is also your first book chapter. It will be the homepage when you render the book.

## Render book

You can render the HTML version of this example book without changing anything:

1. Find the **Build** pane in the RStudio IDE, and

1. Click on **Build Book**, then select your output format, or select "All formats" if you'd like to use multiple formats from the same book source files.

Or build the book from the R console:

```{r, eval=FALSE}
bookdown::render_book()
```

To render this example to PDF as a `bookdown::pdf_book`, you'll need to install XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

## Preview book

As you work, you may start a local server to live preview this HTML book. This preview will update as you edit the book when you save individual .Rmd files. You can start the server in a work session by using the RStudio add-in "Preview book", or from the R console:

```{r eval=FALSE}
bookdown::serve_book()
```

See Figure \@ref(fig:nice-bar).

```{r nice-bar, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', fig.alt='Plot with connected points showing that vapor pressure of mercury increases exponentially as temperature increases.'}

Pie_tipo=Informe_de_virus%>%select(`Object type`)%>%group_by(`Object type`)%>%summarise(n_incidencias = n())
pie3D(Pie_tipo$n_incidencias,labels = Pie_tipo$`Object type`,explode = 0.2,border = "white", main = "Proporcion de inc. por tipo de malware")
```
